The Anatomy of a Hit: Statistically Learning from the Best

### 2024-04-04 paper/paper.qmd
updated paper

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "Modeling the elements that make up top 10 artists' songs"
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/valence-modeling."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "The Anatomy of a Hit: Statistically Learning from the Best"
subtitle: "Modeling the most impactful elements of the most successful musicians."
author: 
  - Luca Carnegie
thanks: "Code and data are available at: https://github.com/lcarnegie/valence-modeling."
date: April 18 2024
date-format: long
abstract: "We attempt to do some interesting things with models and music - stay tuned!"
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---
